Dear Scott, 

We are writing to submit a revised manuscript titled as “Sharing interoperable workflow provenance: A review of best practices and their practical application in CWLProv” to be considered for publication in GigaScience. 

Our work focuses on provenance documentation and standardised representation of bioinformatics workflows to achieve interoperability and reproducibility of workflow-centric data-intensive computational experiments. We have reviewed the existing literature dedicated to devise best practices for workflow design, provenance documentation, analysis sharing and publishing. In the light of these community-driven recommendations, we have devised a generalised hierarchical provenance framework to achieve uniformity in the provenance granularity and completeness in analysis sharing. We have also realized this framework and devised CWLProv - A format for CWL workflow enactment representation using open-source well-defined standards for workflow definition, method aggregation and provenance representation. 

As our contributions can be generalized to any computational scientific workflow-centric study, these are likely to be of interest to wide range of scientific community. The key principles of our research align with the goals of GigaScience i.e. "promoting reproducibility of analyses and data dissemination, organization, understanding, and use". We believe GigaScience is the most appropriate place for publishing our research. 

All authors have approved the manuscript for submission. The work represents original research which is not under consideration by any other journal. We also declare that the content of this manuscript has not been published elsewhere. However an earlier version with preliminary implementation was submitted to IPAW-2018 (10.5281/zenodo.1208478) but was not accepted.

We thank the reviewers for their valuable feedback and GigaScience for giving us this opportunity to implement the changes suggested by the reviewers. We forward hearing from you in due course.
